SAT Competition 2020\tnoteref{title}

### 2020-09-28 paper/main.tex
table of teams and solvers in main tracks

\usepackage[utf8x]{inputenc}
\usepackage[table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{float,lscape}
\usepackage{listings}
\usepackage{tkz-graph}
\lstset{language=C}
\rowcolors{3}{gray!10}{white}

@@

\begin{keyword}
SAT, Competition, Retrospective
\end{keyword}

@@

@@

\section{Selection of Benchmark Instances}

\subsection{Main Instances}

>>>>

\usepackage[utf8x]{inputenc}
\usepackage[table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{float,lscape}
\usepackage[ruled,linesnumbered,vlined]{algorithm2e}
\usepackage{tkz-graph}
\usepackage{lscape}

@@

\begin{keyword}
SAT, Competition
\end{keyword}

@@

%\newcommand{\stack}[2]{\begin{tabular}{@{}c@{}}#1 \\#2\end{tabular}}

% Stack a variable number of arguments:
\makeatletter
\newcommand{\stack}[1]{%
    \begin{tabular}{@{}l@{}}#1\checknextarg}
\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{ \end{tabular}}}
\newcommand{\gobblenextarg}[1]{\\#1\@ifnextchar\bgroup{\gobblenextarg}{ \end{tabular}}}
\makeatother

\begin{table}[h]
\begin{tabular}{|l|l|l|}
\hline
Team & Solver & Configuration / Variant / Hack \\
\hline

\multirow{4}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}} 
 & \multirow{3}{*}{Kissat-sc2020} & --\\
 &  & sat\\
 &  & unsat\\
\cline{2-3}
 & Cadical-sc2020 & --\\
\hline

\multirow{3}{*}{Zhang, Cai}
 & \multirow{3}{*}{Relaxed\_LCMDCBDL} & --\\
 &  & noTimeParam\\
 &  & newTech\\
\hline

\multirow{2}{*}{\stack{Soos, Cai, }{Devriendt, Shaw}}
 & \multirow{2}{*}{CryptoMiniSat-CCAnr} & --\\
 &  & lsids\\
\hline

\stack{Soos, Selman, }{Kautz}~ & CryptoMiniSat-WalkSAT & -- \\
\hline

\multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
 & \multirow{3}{*}{Cadical} & trail\\
 &  & alluip\\
 &  & alluip-trail\\
 \cline{2-3}
 & Maple-LCM-Dist & alluip-trail\\
\hline

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistChronoBT} & f2trc\\
 & & f2trc-s\\
 \cline{2-3}
 & MapleLCMDistChronoBT-DL & f2trc\\
\hline

\stack{Kochemazov, }{Zaikin, }{Kondratiev, }{Semenov} ~& MapleLCMDistChronoBT-DL-v3 & --\\
\hline

\multirow{4}{*}{\stack{Lonlac, }{Nguifo}} & \multirow{4}{*}{Undominated-LC-MapleLCMDistChronoBT-DL} & --\\
 &  & top16\\
 &  & top24\\
 &  & top36\\
\hline

\multirow{5}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{Painless-ExMapleLCMDistChronoBT} & padc\_dl\\
 &  & padc\_dl\_ovau\_lin\\
 &  & padc\_dl\_ovau\_exp\\
 &  & psids\_dl\\
 \cline{2-3}
 & Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

Shaw, Meel & DurianSat & --\\
\hline

\multirow{2}{*}{Chen}
 & Maple & Mix\\
 & Maple & Simp\\
\hline

Riveros & SLIME & --\\
\hline

\multirow{3}{*}{Li, Wu, Xu, Chen} & MLCMDChronoBT-DL-Scavel & --\\
 & MapleLCMDistChronoBT-DL-Scavel01 & --\\
 & MapleLCMDistChronoBT-DL-Scavel02 & --\\
\hline

\multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
 & MapleCOMSPS\_LRB\_VSIDS\_2 & --\\
 & MapleCOMSPS\_LRB\_VSIDS\_2 & LRB\_VSIDS\_2\_init\\
\hline

\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}} & exp-V-LGB-MLD-CBT-DL & --\\
 & exp-V-L-MLDCBT-DL & --\\
 & exp-L-MLD-CBT-DL & -- \\
 & exp-V-MLD-CBT-DL & -- \\
\hline

\multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
 & \multirow{3}{*}{MapleCM} & +dist \\
 &  & +dist+sattime2s+- \\
 &  & +dist+simp2-- \\
 & MapleCMused & +dist \\
\hline

Kaiser, Hartung & PauSat & -- \\
\hline

Osama, Wijs & ParaFROST, ParaFROST-CBT & -- \\
\hline
\end{tabular}
\caption{Teams, Solvers and Hacks participating in the Main Tracks}
\end{table}

@@

\section{Selection and Maintenance of Benchmark Instances}

GBD Tools is a new tool-chain for maintenance and distribuation of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities\footnote{https://pypi.org/project/gbd-tools/} to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.\footnote{\url{https://gbd.iti.kit.edu}}

For selection of benchmarks in this competition, we used a database which contains information about instance author, family and result for a collection of instances used in all SAT competitive events dating back to 2006.\footnote{\url{https://gbd.iti.kit.edu/getdatabase/meta.db}} 
Like this it was possible to query for instances with desired properties, which gives the instance selection process a new quality. 
Using GBD Server, each instance also has an URL, such that instances can also be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.

\subsection{Selection of Instances}

The ``Bring Your Own Benchmarks'' (BYOB) rule (applied as of SAT Competition 2017~\cite{SC2017}) requires solver authors to submit $20$ new benchmark instances in order to participate in the competition. At least $10$ of these instances are required to be ``interesting'', whereby interesting is defined as Minisat~\cite{Niklas:2003:Minisat} needs at least one minute to solve it and the authors own solver does not run into a timeout for the instance.

In total, $28$ authors followed our calls for participation and benchmark instances, thus contributing to a set of $1260$ previously unseen benchmark instances with a variety of $27$ different instance families. 
By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances.

In order to compile a balanced set of $300$ benchmark instances, we used the procedure which is depicted in Algorithm~\ref{algo:select} to select a maximium of $14$ submissions per author. 
Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5-7). 
Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.

\begin{algorithm}[t]
\DontPrintSemicolon

\KwData{$I$ : Set of Instances, $A$ : Set of Authors}
\KwData{Functions $\alpha : I \rightarrow A$ and $\sigma : I \rightarrow \{\mathsf{sat}, \mathsf{unsat}, \mathsf{unknown}\}$}
\KwResult{$S$ : Set of Selected Instances}
\SetKwFunction{rand}{$\mathsf{random.choice}$}
\BlankLine
$S \leftarrow \emptyset$\;

\For {$a \in A$} {
	$I_a^+ \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{sat} \}$, $k=7$}\;	
	$I_a^- \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unsat} \}$, $k=7$}\;	
	\If {$|I_a^+|+|I_a^-| < 14$}{
		$l \leftarrow 14 - (|I_a^+|+|I_a^-|)$\;
		$I_a^? \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unknown} \}$, $k=l$}\;
	}
	$S \leftarrow S \cup I_a^+ \cup I_a^- \cup I_a^?$\;	
}
\Return $S$\;

\caption{Benchmark Instance Selection}
\label{algo:select}
\end{algorithm}

To obtain the final compilation of $400$ benchmark instances, we augmented this set with $100$ instances which have been used in previous competitions. 
We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable and $130$ instances of unkown result. 
Furthermore, we made sure not to select instances of a family which is already represented in the set of newly submitted instances and excluded random, agile and planning instances (due to the planning track).
